\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-14 paper.tex
better abstract / first page

\subsection*{Abstract}
In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes. In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate. Our results indicate that in-ear EEG could provide a discreet, convenient, and usable protocol for multi-factor authentication in a single step, in which a user thinks their chosen passthought.

>>>>

\subsection*{Abstract}
In this paper, we present a system that provides all three factors of authentication (knowledge, possession, and inherence) in a single step, using brain-based authentication via a custom-fit, in-ear EEG. Across all participants, we achieve mean 0\% false acceptance and 0.12\% false rejection rates with data from only one earpiece with three electrodes. In a preliminary test of an "imposter'' spoofing attack, we find a 0\% false acceptance rate. Our results indicate that in-ear EEG could provide a discreet, convenient, and useable protocol for one-step, multi-factor authentication.
